Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-09-05 Manuscript/manuscript.tex
started a table with all simulations

\todo{SAMULI: Table of simulated systems would be useful.}
General simulation setup.

>>>>

\begin{table*}[tbp]
\centering
\caption{  List of MD simulations. 
           Given concentrations adopt the form $C_{bulk}/C_{buffer}$. 
        }
\todo{Joe: to be filled-in. I'll generate it automatically from my Jupyter notebooks.}  
\label{IONsystems_conc}
\begin{tabular}{l c c r r r r }
  lipid/counter-ions &  KCl (mM)  &  NaCl (mM) & CaCl$_2$\,(mM) &  \footnote{Number of lipid molecules with the largest mole fraction}N$_{\rm l}$   &  \footnote{Number of water molecules}N$_{\rm w}$ \todoi{Should confirm that the amounts of water in experiments matched those in simulations.}   &  \footnote{Simulation temperature}T (K)  \\
  \hline
    POPC:POPS (5:1)/K$^+$  & tba & tba & 60:12 & 9999 & 298  \\
    \hline
    POPC:POPS (5:1)/Na$^+$ & tba & tba & 60:12 & 9999 & 298  \\
    \hline
\end{tabular}
\end{table*}

General simulation setup.
